MG7: Configurable and scalable 16S data analysis

### 2016-07-25 docs/mg7-paper/out/paper.tex
add a note for what to add in the assignment correction phase

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  are annotated as being of \texttt{rRNA} type\footnote{We are aware of
    the existence of a gene annotation corresponding to 16S, that we are
    \textbf{not using} due to a significant amount of 16S sequences
    lacking the corresponding annotation}
\item
  their length is at least \texttt{1300}\footnote{Note that 16S
    sequences are sometimes part of an entry corresponding to whole
    small subunits; that's why we do not set a maximum length threshold}
\item
  have at least one taxonomic assignment to a descendant of
  \emph{Bacteria} or \emph{Archaea}
\item
  their lineage does not contain a set of taxa deemed
  uninformative\footnote{for example: ``unclassified Bacteria
    (miscellaneous)'' or ``unclassified''. Assigning a read to an
    ``unclassified'' taxon defeats the first and foremost goal of
    taxonomic profiling: \emph{classification}.}
\end{enumerate}

@@

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  are annotated as being of \texttt{rRNA} type\footnote{We are aware of
    the existence of a gene annotation corresponding to 16S in
    RNACentra, that we are \textbf{not using} due to a significant
    amount of 16S sequences lacking it}
\item
  their length is at least \texttt{1300}\footnote{Note that 16S
    sequences are sometimes part of an entry corresponding to whole
    small subunits; that's why we do not set a maximum length threshold}
\item
  have at least one taxonomic assignment to a descendant of
  \emph{Bacteria} or \emph{Archaea}
\item
  their lineage does not contain a set of taxa deemed
  uninformative\footnote{for example: ``unclassified Bacteria
    (miscellaneous)'' or ``unclassified''. Assigning a read to an
    ``unclassified'' taxon defeats the first and foremost goal of
    taxonomic profiling: \emph{classification}.}
\end{enumerate}

@@

We run MG7 using this set of sequences as query, and with reference all
but the one we are trying to assign. Explain

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  which kind of misassignments can be detected
\item
  how
\item
  why it is OK for sequences assigned to strange taxa, with no close 16S
  seq (they will get no hits)
\item
  we analyze every assignment independently
\end{enumerate}
